miceEXTRA

### 2024-03-23 miceEXTRA.Rmd
put extra imputation tests etc for mice into another file

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(naniar))
suppressPackageStartupMessages(library(mice))

```{r setup, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

# loaded data set for module 2 eco -pol variables and removes the rows with question number and question text
```

```{r, eval =TRUE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule2 <- module2 %>%

#remove row 1
  filter(!row_number() %in% c(1,2)) %>%

# replace risky likert scale with numbers
  mutate_at(vars(starts_with("Risky")), funs(case_when(. =="Not at all risky" ~ 1, 
                                                       . =="Slightly risky" ~ 2, 
                                                       . =="Moderately risky" ~ 3, 
                                                       . =="Very risky" ~ 4, 
                                                       . =="Extremely risky" ~ 5))) %>%

# replace beneficial likert scale with numbers  
  mutate_at(vars(starts_with("Ben")), funs(case_when(. =="Not at all beneficial" ~ 1,
                                                     . =="Slightly beneficial" ~ 2,
                                                     . =="Moderately beneficial" ~ 3,
                                                     . =="Very beneficial" ~ 4,
                                                     . =="Extremely beneficial" ~ 5 ))) %>%

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# NO reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                               . == "Somewhat disagree" ~ 2,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 4,
                                                               . == "Strongly agree" ~ 5))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# NO reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

# Bar plot: STATE X PDEVELOP

```{r}

# Load necessary libraries
library(dplyr)
library(ggplot2)
library(forcats)

# Df to include relevant variables

WBques <- module2 %>%  filter(!row_number() %in% c(1,2)) %>% dplyr::select(State, DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR ) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

levels_defined <- c("Strongly agree", "Somewhat agree","Neither agree nor disagree", "Somewhat disagree","Strongly disagree","Rather not say/Don't know")

WBques_factors <- WBques
WBques_factors[] <- lapply(names(WBques_factors), function(colname) {
  if (colname != "State") {
    factor(WBques_factors[[colname]], levels = levels_defined)
  } else {
    WBques_factors[[colname]] # Keep the State column unchanged
  }
})

WBques_factors$State <- factor(WBques_factors$State, 
                               levels = c("West Bengal", "Uttar Pradesh", "Maharashtra", "Rajasthan", "Tamil Nadu"))

library(dplyr)
library(ggplot2)

# Assuming your updated data frame is named WBques_factors

# Create a summary table with counts for each level of DISPLACENUCLEAR within each State
WBques_summary <- WBques_factors %>%
  count(State, DISPLACENUCLEAR) %>%
  group_by(State) %>%
  mutate(Proportion = n / sum(n))

# Create a named vector with full statements for each variable
full_statements <- c(DISPLACENUCLEAR = "Nuclear energy is leading to displacement of people from their land",
                     BEAUTYNUCLEAR = "Nuclear energy spoils the natural beauty of the landscape",
                     POLLUTENUCLEAR = "Nuclear energy increases pollution of air/water/land",
                     HEALTHNUCLEAR = "Nuclear energy poses a great risk to the health of people living around it",
                     ENVOVERDEV = "Polluting industries that spoil the environment should be shut down even if it costs people their jobs")

# Reshape the data to long format for the selected variables
WBques_long <- WBques_factors %>%
  pivot_longer(cols = c(DISPLACENUCLEAR, HEALTHNUCLEAR, BEAUTYNUCLEAR, POLLUTENUCLEAR),
               names_to = "Question",
               values_to = "Response") %>%
  mutate(Question = recode(Question, !!!full_statements)) # Replace var names with full statements

# Create a summary table with proportions for each level of Response within each State and Question
WBques_summary <- WBques_long %>%
  count(State, Question, Response) %>%
  group_by(State, Question) %>%
  mutate(Proportion = n / sum(n))

# Define the color sequence, with the darkest red for "Strongly agree"
colorsequence <- c("#8C4646","#D9695F","#F2A679","#F2D091","#FFF2CC","#808080")

# Plot the graph with facets for each Question
ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_manual(values = rev(colorsequence), name = NULL) +
  facet_wrap(~ Question, scales = "free_y", ncol = 1) +
  coord_flip() +
  labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
  theme_minimal() +
  theme(
    # Increase the size of the main title
    plot.title = element_text(size = 16, face = "bold"),
    # Increase the size of the axis titles
    axis.title = element_text(size = 14),
    # Increase the size of the facet strip text
    strip.text.x = element_text(size = 12),
    # Adjust text angle for State labels if necessary
    axis.text.y = element_text(angle = 0)
  )

# barplot of demographics

library(dplyr)
library(tidyr)

demobar <- codedmodule2 %>% 
  dplyr::select("State", "Language", "age", "urban_rural", "gender", "caste" ,"religion") %>%
              mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
              mutate_all(~ifelse(. == "OBC", "Other Backward Classes (OBC)", .))%>%
              mutate_all(~ifelse(. == "SC", "Scheduled caste (SC)", .))%>%
              mutate_all(~ifelse(. == "ST", "Scheduled tribe (ST)", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "TA", "Tamil", .)) %>%
              mutate_all(~ifelse(. == "EN", "English", .))%>%
              mutate_all(~ifelse(. == "BN", "Bengali", .))%>%
              mutate_all(~ifelse(. == "MAR", "Marathi", .))%>%
              mutate_all(~ifelse(. == "HI", "Hindi", .))%>%
              na.omit()

#changing factor levels for each variable from high to low n

demobar$State <- factor(demobar$State, levels = c("Rajasthan", "Maharashtra","West Bengal" , "Tamil Nadu", "Uttar Pradesh"))
demobar$Language <- factor(demobar$Language, levels = c("Hindi","Marathi","Bengali","Tamil", "English"))
demobar$age <- factor(demobar$age, levels = c( "18-24 years old" ,  "25-34 years old","35-44 years old", "45-54 years old", "55-64 years old","65-74 years old","75 years or older"  ))
demobar$urban_rural <- factor(demobar$urban_rural, levels = c("Rural","Urban"))
demobar$gender <- factor(demobar$gender, levels = c("Male","Female"))
demobar$caste <- factor(demobar$caste, levels = c("Scheduled tribe (ST)", "Scheduled caste (SC)", "Other Backward Classes (OBC)", "General","Brahmin","Rather not say/Don't know"))
demobar$religion <- factor(demobar$religion, levels = c("Hinduism", "Islam", "Christanity","Buddhism","Agnostism/ Atheism","Other (Please mention)"))

```{r, echo=FALSE, fig.width=11, fig.height=14, out.width='80%', out.height='80%'}

# Loading the required libraries
library(tidyverse)
library(gridExtra)
library(scales)

# Function to create bar plot
create_bar_plot <- function(data, variable_name, palette_name) {
  factor_levels <- levels(demobar[[variable_name]])
  data %>%
    filter(Variable == variable_name) %>%
    mutate(Category = factor(Category, levels = factor_levels)) %>%
    ggplot(aes(y = "", x = Percentage, fill = Category)) +
    geom_bar(position = "fill", stat = "identity", width = 1) +
    geom_text(aes(label = paste0(round(Percentage, 0), "%")), 
              position =  position_fill(vjust = 0.5)) +
    scale_x_continuous(labels = percent) +
    labs(y = NULL, x = "Percentage", fill = variable_name) +
    theme_classic() +
    theme(axis.text.y = element_blank(), strip.text = element_text(size = 10), legend.position = "top") +
    scale_fill_brewer(palette = palette_name)
}

# Gather data to long format and calculate counts and percentages
df_barplot <- demobar %>%
  gather(Variable, Category) %>%
  group_by(Variable, Category) %>%
  filter(!is.na(Category)) %>%
  summarise(n = n()) %>%
  mutate(Percentage = n / sum(n) * 100)

# Create separate plots for each variable
plot_state <- create_bar_plot(df_barplot, "State", "Spectral")
plot_language <- create_bar_plot(df_barplot, "Language", "Paired")
plot_age <- create_bar_plot(df_barplot, "age", "Set3")
plot_urban_rural <- create_bar_plot(df_barplot, "urban_rural", "Dark2")
plot_gender <- create_bar_plot(df_barplot, "gender", "Pastel1")
plot_caste <- create_bar_plot(df_barplot, "caste", "Set1")
plot_religion <- create_bar_plot(df_barplot, "religion", "Set2")

# Combine the plots with spacing
combined_plot <- gridExtra::arrangeGrob(plot_state, plot_language, plot_age, plot_urban_rural, plot_gender, plot_caste, plot_religion, ncol = 1, heights = c(1, 1, 1, 1, 1, 1, 1))

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

# Can do something with accept, reject and reluctantly accept.

## Can do something with accept, reject and reluctantly accept.

n_acceptreject<- module2 %>%
                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

summary(n_acceptreject)
```

# missing data pattern and MCAR

formice1 <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|DEVOVERENV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext")) %>%
          mutate(across(age, ~factor(.x, ordered = TRUE)))%>%  
          mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
          mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
          mutate(Uppercaste = ifelse(caste %in% c('Brahmin', 'General'), 1, 0)) %>%
          mutate(Male = ifelse(gender == 'Male', 1, 0))%>%
          mutate(Hindu = ifelse(religion == 'Hinduism', 1, 0))%>%
          mutate(Age = case_when(
                                  age == "18-24 years old" ~ 1,
                                  age == "25-34 years old" ~ 2,
                                  age == "35-44 years old" ~ 3,
                                  age == "45-54 years old" ~ 4,
                                  age == "55-64 years old" ~ 5,
                                  age == "65-74 years old" ~ 6,
                                  age == "75 years or older" ~ 7))

#dplyr:: select(starts_with (c("State", "age", "urban_rural", "gender", "caste", "religion","Risky_Solar", "Risky_Nuclear", "Risky_Coal", "Ben_Solar","Ben_Nuclear","Ben_Coal","K_S","K_E","K_H","K_I", "DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEV", "PROSPER", "RELY", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "OWNERREG", "DECISIONCEN","INDUSTRYLARGE","ECONOMYGLOBAL","OWNERPVT","OWNERNOREG" )))

library(dplyr)

formice <- formice1 %>%
  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
  mutate(across(State, ~factor(.x, ordered = FALSE)))

#str(formice)
summary(formice)

# litte's MCAR test

sum(is.na(formice))

mcar_test(data= codedmodule2)

# p value = 1, which means MAR condition is met.

# Kahan scale: MAR condition and missing data pattern 
```{r, echo=FALSE}

kahanall <- codedmodule2 %>%
          dplyr::select(c(starts_with("K_"), "age", "gender", "caste", "State", "urban_rural", "religion")) %>%
          mutate(across(gender:religion, ~factor(.x, ordered = FALSE))) %>%
          mutate(across(age, ~factor(.x, ordered = TRUE)))

str(kahanall)

md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1

mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met

# dataset with missing variables to compare and test group comaprisons

MARkahan <- codedmodule2 %>%
          dplyr::select(c("K_SHARM", "K_IPROTECT", "K_IPRIVACY", "K_SPROTECT", "K_SLIMCHOI", "K_IINTRFER",  "K_HEQUAL", "K_HREVDIS1" , "age", "gender", "caste", "State", "urban_rural", "religion"))

MARkahan$K_SHARM_MAR <- MARkahan$K_SHARM

MARkahan$K_IPROTECT_MAR <- MARkahan$K_IPROTECT

MARkahan$K_SPROTECT_MAR <- MARkahan$K_SPROTECT

MARkahan$K_SLIMCHOI_MAR <- MARkahan$K_SLIMCHOI

library(finalfit)

# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SHARM_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SHARM variable.")

#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_IPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_IPROTECT variable.")

#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SLIMCHOI_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

## Mifa for Kahan scale 
```{r, echo =FALSE}

library(mifa)
library(mice)
library(psych)

mikahan <- mifa(data= kahanall,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m = 50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 427,)

mikahan

library(psych)

fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit, sort= TRUE, cut= 0.4)

kahanfit4 <- psych::fa(mikahan$cov_combined, nfactors = 3, rotate = "varimax")

print.psych(kahanfit4, sort= TRUE, cut= 0.4)

## Pretty Table: FA Kahan

library(flextable)

flex <- function(data, title=NULL, col_widths=NULL) {
  tbl <- flextable(data) %>%
           #padding(padding = 1, part = "all") %>%
           #set_table_properties(layout = "autofit") %>%
           fontsize(size=10, part="all") %>%
           set_caption(title, 
                       autonum = officer::run_autonum(seq_id = "tab", 
                                                      pre_label = "Table ", 
                                                      post_label = "\n", 
                                                      bkm = "anytable"))

  # If col_widths is provided, set column widths
  if(!is.null(col_widths)) {
    for(col in names(col_widths)){
      tbl <- width(tbl, j = col, width = col_widths[[col]])
    }
  }

  return(tbl)
}

rename_map <- c(
  "K_SHARM" = " (C)Sometimes the government needs to make laws that keep people from hurting themselves.",
"K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s
good for society.",
"K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and
choices of individuals.",
"K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
"K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
"K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
"K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",
"K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
"K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
"K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
"K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
"K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
)

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #suppress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")

  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      code = names(rename_map)[match(item, rename_map)], # extracting short form
      across(where(is.numeric), round, 3)
    ) %>%
    dplyr::select(code, everything()) # reorder columns to bring code to the front
}

fa_table(fit , .4) %>%
  rename(Egalitarianism = MR1, Communitarianism = MR2, Items= item, Code= code) %>%
  flex("Table 1: EFA on adapted Cultural Cognition Scale from Kahan et al(2007)", col_widths = list(Items = 4.5, Code = 1))

```{r, echo = FALSE}
fit[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
  rename(Egalitarianism = MR1, Communitarianism = MR2) %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Table 2: Eigenvalues and Variance Explained for Cultural Cognition Scale")
```

## checking merging of imputations  : kahan scale

kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)

kahan_imp$chainMean

#Kahan Factor scores: mean across all imputations

kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")

kahanallscores <- kahanallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

str(kahanallscores)

nkahanall <- kahanallscores %>%
  rowwise() %>%
  mutate(
    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2"))),
    K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

nkahanfinal <- data.frame(factor.scores(nkahanall[, 1:12], fit)$scores)

## Kahan corelation table
```{r}

cor(nkahanall)

#before mice 
 cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))

#after mice
 cor.plot(nkahanall)

cov(nkahanall)

## Kahan scater plot from EFA scores 
```{r, echo = FALSE}

nkahanfinal %>%
  ggplot(aes(MR1, MR2))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=0, colour="black", lwd=0.5)+
  geom_vline(xintercept=0, colour="black", lwd=0.5)+
  labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
  ylim(-2,3)+
  xlim(-2,3)+
  theme_minimal() 
```

# Kahan alpha test

KahanallHE <-nkahanall %>%
  dplyr::select(starts_with(c("K_H", "K_E")))

KahanallHE_alpha <- psych::alpha(KahanallHE, check.keys = TRUE) # alpha = 0.71

KahanallC <-nkahanall %>%
  dplyr::select(starts_with(c("K_S")))

KahanallC_alpha <- psych::alpha(KahanallC, check.keys = TRUE) # alpha = 0.73

@@

# Eco-pol scale: MAR condition and missing data pattern

ecopoln <- formice1 %>%
  dplyr::select(
    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State
  )

md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR

mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met

# dataset with missing variables to compare and test group comaprisons

MARecopol <- codedmodule2 %>%
          dplyr::select(c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State))

MARecopol$JOBSNUCLEAR_MAR <- MARecopol$JOBSNUCLEAR

MARecopol$PRIDENUCLEAR_MAR <- MARecopol$PRIDENUCLEAR

library(finalfit)

# JOBSNUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "JOBSNUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the JOBSNUCLEAR variable.")

# PRIDENUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "PRIDENUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the PRIDENUCLEAR variable.")

## Mifa for new eco-pol value scale : Nuclear energy

miecopol <- mifa(data= ecopoln,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

miecopol

ecopolfit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfit2, sort= TRUE, cut= 0.4)

#Ecopol Factor scores: mean across all imputations

ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 50, seed = 429, print = FALSE), "broad")

ecopolallscores <- ecopolallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

#str(ecopolallscores)

necopol <- ecopolallscores %>%
  rowwise() %>%
  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

necopolfinal <- data.frame(factor.scores(necopol[, 1:24], ecopolfit2)$scores)

# Eco-pol alpha test

nPdevelop <-necopol %>%
  dplyr::select((c(BEAUTYNUCLEAR,  HEALTHNUCLEAR,  POLLUTENUCLEAR, DISPLACENUCLEAR, OWNERPUB, ENVOVERDEV)))

nPdevelop_alpha <- psych::alpha(nPdevelop, check.keys = TRUE) # alpha = 0.79

nNdevelop <-necopol %>%
  dplyr::select((c(DEVNUCLEAR, PROSPERNUCLEAR,PRIDENUCLEAR, NPRIDENUCLEAR, JOBSNUCLEAR, ECONOMYGLOBAL,          WEALTHLIM,INDUSTRYLARGE, DECISIONCEN, MECHANISATION )))

nNdevelop_alpha <- psych::alpha(nNdevelop , check.keys = TRUE) # alpha = 0.79

# Eco-pol: Radar map

```{r, echo=FALSE}
library(ggplot2)
library(fmsb)

nrow(ecopolfit2$loadings)

# Extract the loadings
loadings_matrix4 <- ecopolfit2$loadings[1:24, ]

loadings_df2 <- as.data.frame(as.matrix(loadings_matrix4))

# Adding rownames to the dataframe as a new column
loadings_df2 <- loadings_df2 %>%
  rownames_to_column(var = "variable")

>>>>

---
title: "miceEXTRA"
output: html_document
---

# EXTRA

@@
